---
title: "EDS221_Day7_Joins_Activities"
author: "OP"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(janitor)
libreary(here)
```


## Create some data, check the classes, index!
### Vectors, lists & data frames

#### In your Quarto document:

1. Create a vector called vec_1 containing the following:
2, 5, 9, 10, 8, 12, 1, 0
```{r}
vec_1 <- c(2, 5, 9, 10, 8, 12, 1, 0)
vec_1
```


2. Check the following for that vector:

2.1 What is the class of the vector? class()
```{r}
class(vec_1)
```

2.2 What type of variable does it store? typeof()
```{r}
typeof(vec_1)
```

2.3 Access the 3rd element and store as vec_1_e3
```{r}
vec_1_e3 <- vec_1[3]
vec_1_e3
```


2.4 Access the 1st element and store as vec_1_e1
```{r}
vec_1_e1 <- vec_1[1]
vec_1_e1
```

2.5 Access the 5th through 7th elements and store as vec_1_e5to7
```{r}
vec_1_e5to7 <- vec_1[5 : 7]
vec_1_e5to7
```

2.6. Reassign vec_1 as a character using as.character, stored as vec_1_char. What does the output look like?
```{r}
vec_1_char <- as.character(vec_1)
vec_1_char
```


2.7. Create a vector called vec_2
vec_2 should contained named elements, where town = "Santa Barbara, location = "Rincon", swell = "south"
```{r}
vec_2 <- c(town = "Santa Barbara", location = "Rincon", swell = "south")
vec_2
```

2.8 What is the class of vector elements? class()
```{r}
class(vec_2)
```


2.9 What is the length of vec_2?
```{r}
length(vec_2)
```

2.10 Access the 2nd element by name and store as vec_2_e2
```{r}
vec_2_e2 <- vec_2[[2]]
vec_2_e2
```

3. Create a data frame in R, index
Write code to create a data frame called df_1 that looks like this:
   region     species count
 1      A       otter    12
 2      B great white     2
 3      A    sea lion    36
 4      D  gray whale     6

```{r}
df_1 <- data.frame(region = c("A", "B", "A", "D"), species = c("otter", "great white", "sea lion", "gray whale"), count = c(12, 2, 36, 6))
df_1
```

3.1 Return the class of the entire data frame
```{r}
class(df_1)
```

3.2 Return the class of the species column
```{r}
class(df_1$species)
```

3.3 Find the maximum value of the count() column, store as max_count
```{r}

max_count <- max(df_1$count)
max_count
```


