---
title: "string_practice"
format: html
editor: visual
---

```{r}
library(datapasta)
library(tidyverse)
```


## Task 3: Practice with strings
Create a new .qmd in your R folder called string_practice.qmd
Copy all contents of the html table below to your clipboard:

date	building	alarm_message
2020-03-14	Engineering-North	10:02am – HVAC system down, facilities management alerted
2020-03-15	Bren Hall	8:24am – Elevator North out of service
2020-04-10	Engineering-South	12:41am – Fire alarm, UCSB fire responded and cleared
2020-04-18	Engr-North	9:58pm – Campus point emergency siren, UCPD responded

```{r}
alarm_report <- data.frame(
  stringsAsFactors = FALSE,
              date = c("2020-03-14", "2020-03-15", "2020-04-10", "2020-04-18"),
          building = c("Engineering-North",
                       "Bren Hall","Engineering-South","Engr-North"),
     alarm_message = c("10:02am – HVAC system down, facilities management alerted",
                       "8:24am – Elevator North out of service",
                       "12:41am – Fire alarm, UCSB fire responded and cleared",
                       "9:58pm – Campus point emergency siren, UCPD responded")
)
```

Practice working with strings by writing code to update alarm_report as follows (these can be separate, or all as part of a piped sequence):

1. Replace the “Engr” with “Engineering” in the building column
```{r}
alarm_report <- alarm_report %>% 
  mutate(building = str_replace(building, "Engr", "Engineering"))
```


2. Separate the building column into two separate columns, building and wing, separated at the dash
```{r}
alarm_report <- alarm_report %>%
  separate(building, into = c("building", "wing"), sep = "-")
```


3. Only keep observations with the word “responded” in the alarm_message column
```{r}
alarm_report_subset <- alarm_report %>%
  filter(str_detect(alarm_message, "responded"))

```


4. Separate the message time from the rest of the message by separating at --
```{r}
alarm_report_time <- alarm_report %>%
  separate(alarm_message, into = c("time", "message"), sep = " – ")
  
```


5. Convert the date column to a Date class using lubridate
```{r}
alarm_report_time %>%
  mutate(date = lubridate::ymd(date)) %>% 
  relocate(time, .after = "date")
```

